Safe Transferable Regions

### 2016-10-22 paper/type-inference.tex
Removed claims of completeness.

Let $\consOf{q}$ denote the set of constraints generated from an elaborated program $q$.
The following theorem states that constraint-generation is sound and complete:
\begin{theorem}
\label{thm:constraint-generation-sc}
Let $C = \consOf{q}$.
An assignment $\soln$ (for the region and predicate variables in $q$)
satisfies $C$ iff $q[\soln]$ is well-typed.
\end{theorem}

@@

Theorems~\ref{thm:constraint-generation-sc} and~\ref{thm:constraint-solver-sc}
show that the second and third steps of the type-inference algorithm are both
sound and complete.
It is easy to verify the soundness of the first step (the elaboration phase):
For any program $p \in \absof{\FB}$, the elaboration phase produces a $q$
such that for any assignment $\soln$, we have $\absof{q[\soln]} = p$.
%
The soundness of the type inference algorithm follows.
The only sources of incompleteness in the type inference algorithm are some heuristic
choices made in the first step, as explained below.

@@

If users provide partial region annotations, especially in situations (such as above) where elaboration
makes a heuristic choice, the elaboration procedure can use the user-provided choices instead.
This can help the type-inference overcome these sources of incompleteness.

>>>>

Let $\consOf{q}$ denote the set of constraints generated from an elaborated program $q$.
The following theorem states that constraint-generation is sound:
\begin{theorem}
\label{thm:constraint-generation-sc}
Let $C = \consOf{q}$.
An assignment $\soln$ (for the region and predicate variables in $q$)
satisfies $C$ only if $q[\soln]$ is well-typed.
\end{theorem}

@@

Theorem~\ref{thm:constraint-generation-sc}
and~\ref{thm:constraint-solver-sc} show that the second and third
steps of the type-inference algorithm are sound. It is easy to verify
the soundness of the first step (the elaboration phase): For any
program $p \in \absof{\FB}$, the elaboration phase produces a $q$ such
that for any assignment $\soln$, we have $\absof{q[\soln]} = p$.
%
The soundness of the type inference algorithm follows.
Theorem~\ref{thm:constraint-solver-sc} also establishes the
completeness of constraint solving.

The main source of incompleteness in the type inference algorithm is
the set of heuristic choices made during region parameterization step,
as explained below.

@@

If users provide partial region annotations, especially in situations (such as above) where elaboration
makes a heuristic choice, the elaboration procedure can use the user-provided choices instead.
This can help the type-inference overcome these limitations.
